A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Minor improvements in shift-reduce section

A shift-reduce parser accepts a sequence of input tokens $\mathbf x = (x_1, \dots, x_N)$ and uses transitions $\mathbf t = (t_0, \dots, t_{T-1})$, where each $t_t \in \{\shift, \reduce\}$ specifies a \shift~or \reduce~transition (described below). In general a parser may also generate these predictions on-the-fly as it reads the tokens. It reads left-to-right over the input transition sequence, combining the input tokens $\mathbf x$ incrementally into a tree structure. For any binary-branching tree structure over $N$ words, this requires $T = 2N - 1$ transitions.

The parser uses two auxiliary data structures, a stack $S$ of partially completed subtrees and a buffer $B$ of tokens yet to be parsed. The parser is initialized with the stack empty and with the buffer containing the tokens $\mathbf x$ of the sentence in order. Let $\langle S, B \rangle = \langle \emptyset, \mathbf x \rangle$ denote this starting state. We next proceed through the transition sequence, where each transition $t_t$ selects one of the two following operations. Below the $\mid$ symbol denotes the \textit{cons} (concatenation) operator. We arbitrarily choose to always \textit{cons} on the left in the notation below.
\begin{description}
  \item[\shift:] $\langle S, x \mid B \rangle \to \langle x \mid S, B \rangle$. This operation pops an element from the buffer and pushes it onto the top of the stack.
  \item[\reduce:] $\langle x \mid y \mid S, B \rangle \to \langle (x, y) \mid S, B \rangle$. This operation pops the top two elements from the stack, merges them into a binary tree with children $(x, y)$, and pushes the result back onto the stack.
\end{description}

>>>>

A shift-reduce parser accepts a sequence of input tokens $\mathbf x = (x_1, \dots, x_N)$ and uses transitions $\mathbf t = (t_0, \dots, t_{T-1})$, where each $t_t \in \{\shift, \reduce\}$ specifies a parser transition (described below). In general a parser may also generate these predictions on-the-fly as it reads the tokens. It proceeds left-to-right through a transition sequence, combining the input tokens $\mathbf x$ incrementally into a tree structure. For any binary-branching tree structure over $N$ words, this requires $2N - 1$ transitions.

The parser uses two auxiliary data structures: a stack $S$ of partially completed subtrees and a buffer $B$ of tokens yet to be parsed. The parser is initialized with the stack empty and with the buffer containing the tokens $\mathbf x$ of the sentence in order. Let $\langle S, B \rangle = \langle \emptyset, \mathbf x \rangle$ denote this starting state. We next proceed through the transition sequence, where each transition $t_t$ selects one of the two following operations. Below the $\mid$ symbol denotes the \textit{cons} (concatenation) operator. We arbitrarily choose to always \textit{cons} on the left in the notation below.
\begin{description}
  \item[\shift:] $\langle S, x \mid B \rangle \to \langle x \mid S, B \rangle$. This operation pops an element from the buffer and pushes it onto the top of the stack.
  \item[\reduce:] $\langle x \mid y \mid S, B \rangle \to \langle (x, y) \mid S, B \rangle$. This operation pops the top two elements from the stack, merges them into a binary tree with children $(x, y)$, and pushes the result back onto the stack.
\end{description}
